### 2019-09-24 management.tex
updates management

$\textbf{Account Coordinator}$\\
$\textbf{Registration Coordinator}$\\
$\textbf{Sponsorship Coordinator}$\\

@@

$\textbf{Technical Subcommittee Chair}$\\
$\textbf{Sessions Coordinator}$\\
$\textbf{Workshops Coordinator}$\\
$\textbf{Career Fair Coordinator}$\\

@@

$\textbf{Logistics Chair}$\\
$\textbf{Hotels and Transportation Coordinator}$\\
$\textbf{Hospitality and Catering Coordinator}$\\
$\textbf{Tours Coordinator}$\\
$\textbf{Program Coordinator}$\\

$\textbf{Media Coordinator}$\\

>>>>

\setlength\intextsep{0pt}
\begin{wrapfigure}{R}{0.35\textwidth}
	\begin{center}
		\vspace{-\baselineskip}
		\includegraphics[height=15\baselineskip]{stahlj.jpg}
	\end{center}
\end{wrapfigure}
$\textbf{Account Coordinator - Jack Stahl}$\\

\setlength\intextsep{0pt}
\begin{wrapfigure}{R}{0.35\textwidth}
	\begin{center}
		\vspace{-\baselineskip}
		\includegraphics[height=15\baselineskip]{dinarij.jpg}
	\end{center}
\end{wrapfigure}
$\textbf{Registration Coordinator - Jasmine Dinari}$\\

\setlength\intextsep{0pt}
\begin{wrapfigure}{R}{0.35\textwidth}
	\begin{center}
		\vspace{-\baselineskip}
		\includegraphics[height=15\baselineskip]{sheheej.jpg}
	\end{center}
\end{wrapfigure}
$\textbf{Sponsorship Coordinator - James Shehee}$\\

@@

\setlength\intextsep{0pt}
\begin{wrapfigure}{R}{0.35\textwidth}
	\begin{center}
		\vspace{-\baselineskip}
		\includegraphics[height=15\baselineskip]{cheeg.jpg}
	\end{center}
\end{wrapfigure}
$\textbf{Technical Subcommittee Chair- Gwen Chee}$\\

\setlength\intextsep{0pt}
\begin{wrapfigure}{R}{0.35\textwidth}
	\begin{center}
		\vspace{-\baselineskip}
		\includegraphics[height=15\baselineskip]{fairhurstr.jpg}
	\end{center}
\end{wrapfigure}
$\textbf{Workshops Coordinator - Roberto Fairhurst}$\\
Roberto graduated with a B.S. in Nuclear Engineering from Instituto Balseiro (Argentina) April 2018. He is now a 2nd-year graduate student at UIUC. He does research on computational multi-physics solvers applied to advanced reactors as part of the Advanced Reactors and Fuel Cycle group under the supervision of Dr. Kathryn Huff. He got experience in the organization of conferences during the planning and development of a technical workshop (TWOFCS19) that took place at UIUC in June 2019. His motivation for hosting a student conference is his passion for Nuclear Energy and his desire to transmit this passion to other students. He believes hosting the student conference at UIUC will help the field grow and thrive. This is also an opportunity to meet other people working in the field, share life experiences, and develop a stronger network.

$\textbf{Sessions Coordinator - Zachary Jeckell}$\\
$\textbf{Career Fair Coordinator - Greg Golba}$\\

@@

\setlength\intextsep{0pt}
\begin{wrapfigure}{R}{0.35\textwidth}
	\begin{center}
		\vspace{-\baselineskip}
		\includegraphics[height=15\baselineskip]{gaughann.JPG}
	\end{center}
\end{wrapfigure}

$\textbf{Logistics Chair - Natalie Gaughan}$\\
Natalie earned her B.S. in Nuclear Engineering from the University of Wisconsin-Madison in 2017. She has completed internships at Argonne National Laboratory and the International Atomic Energy Agency. She is now a graduate student at UIUC intending to research radiological science and nuclear medicine. Natalie has attended two ANS student conferences in the past and knows how these conferences can be influential in students’ career development. She will be attending the upcoming ANS student conference in 2020 at NC State.

\setlength\intextsep{0pt}
\begin{wrapfigure}{L}{0.35\textwidth}
	\begin{center}
		\vspace{-\baselineskip}
		\includegraphics[height=15\baselineskip]{kdilan.jpg}
	\end{center}
\end{wrapfigure}
$\textbf{Program Coordinator - Dilan Kurukulasuriya}$\\
Dilan Kurukulasuriay is a second-year undergraduate student pursuing a B.S. in Nuclear, Plasma, and Radiological Engineering, along with a minor in Physics and Mathematics. He has been active in ANS at UIUC since the start of his freshman year, and he currently serves as the Outreach Chair on the Executive Board. Dilan has worked at the Center for Plasma-Material Interactions lab since the start of his freshman year on HIDRA, and he stayed on campus over the summer to continue to do so. Dilan attended the 2019 ANS Student Conference and it was the highlight of his freshman year of college. He is interested in fusion science research, specifically the materials interaction aspect. He also plans on attending the upcoming student conference at NC State in 2020.

\setlength\intextsep{0pt}
\begin{wrapfigure}{R}{0.35\textwidth}
	\begin{center}
		\vspace{-\baselineskip}
		\includegraphics[height=15\baselineskip]{davisg.jpg}
	\end{center}
\end{wrapfigure}
$\textbf{Hotels and Transportation Coordinator - Gavin Davis}$\\

\setlength\intextsep{0pt}
\begin{wrapfigure}{R}{0.35\textwidth}
	\begin{center}
		\vspace{-\baselineskip}
		\includegraphics[height=15\baselineskip]{moranb.jpg}
	\end{center}
\end{wrapfigure}
$\textbf{Hospitality and Catering Coordinator - Brady Moran}$\\

\setlength\intextsep{0pt}
\begin{wrapfigure}{R}{0.35\textwidth}
	\begin{center}
		\vspace{-\baselineskip}
		\includegraphics[height=15\baselineskip]{ballaa.jpg}
	\end{center}
\end{wrapfigure}
$\textbf{Tours Coordinator - Anna Balla}$\\

\setlength\intextsep{0pt}
\begin{wrapfigure}{L}{0.35\textwidth}
	\begin{center}
		\vspace{-\baselineskip}
		\includegraphics[width=0.3\textwidth]{ryann.jpg}
	\end{center}
\end{wrapfigure}
$\textbf{Media Coordinator - Nathan Ryan}$\\
Nathan is pursuing a B.S. in Physics from UIUC. He graduated in the top five of his high school class, while holding down a part time managerial position and running a research project at Argonne National Laboratory concurrent with his Sophomore through Senior years of Secondary Education. His first experience with Nuclear Physics was at the National Superconducting Cyclotron Laboratory where he worked with grad students on rare Cadmium isotopes. He has experience with building appealing website pages, as well as social media communications. He believes that an online presence for this event will supplement the success of an already great set of programs and individuals involved. He is excited to attend the upcoming ANS Student Conference at NC State in 2020.
